Universal Anonymous Signatures

### 2022-06-16 prism-backend/research/gsac/app-model-related.tex
Refined definition for unforgeability in DAC, and proof.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with $\opk'$ from \parm as opener public key.
\end{description}

@@

\begin{theorem}[Anonymity of \CUASAC]
  If the base \CUASGen construction is anonymous according to
  \defref{def:anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~ against anonymity of \CUASAC as defined in \cite{fhs19}, we build
  an adversary \advB against anonymity of \CUASGen as defined in
  \defref{def:anonymity-uas}.

@@

\begin{theorem}[Unforgeability of \CUASAC]
  If the base \CUASGen construction has sign unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
\end{theorem}

@@

To showcase the feasibility of building delegatable anonymous credentials (DAC)
from \UAS, we give a simple definition for a DAC scheme, extending
\cite{fhs19} and inspired by \cite{bcc+09}. Note however that, unlike the
latter, our simple scheme built from \CUASGen does not ensure privacy of the
delegation chain -- but it does, however, ensure that a (not top-level) issuer
can only delegate attributes contained in a credential it owns. Also, for
simplicity, we restrict to the case of using one credential per
signature/interactive credential presentation, and assume that all parties use
the same opener and \finsp function.
%
The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $Obtain,Issue$ and
$Show,Verify$ interactive protocols.
%
In the modelling for this setting, since there are multiple issuers, in addition
to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
issuers, and corrupt existing ones, respectively. The issuance and sign
anonymity properties are as before. For unforgeability, we still require
that no adversary can authenticate using a set of attributes that have not been
issued to a corrupt user. In addition, we require that for any possible
successful authentication protocol using a level-$n$ credential, we can extract
a chain of credentials of length $n$ such that each level-$i$ credential can
be used successfully to authenticate a level-$(i+1)$ credential up to the
level-$n$ credential, and that the attributes revealed in the level-$n$
authentication are contained in all the credentials up the chain.

% \todo{Rewrite when the full rewriting of the paper is done. For now, just
%   adapting the construction.}
% We give a simple definition for delegatable anonymous credentials extending
% the anonymous credential model in \cite{fhs19}, but drawing inspiration from
% \cite{bcc+09}. Next, we briefly describe a construction based on $(\fissue^n,
% \feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
% show that it satisfies our basic notion of delegatable anonymous credentials.
% Roughly, a delegatable anonymous credential scheme is an anononymous credential
% scheme in which every issuer of level $n$ can only issue credentials of level
% $n+1$. For simplicity, we restrict to the case of using only one credential per
% signature, but the generalization is trivial. Note that, in addition to the
% algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
% which, given an issuer's public key and its alleged level, returns $1$ if the
% level is correct, or $0$ otherwise.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        %(\opk,\osk) \gets \OKeyGen(\parm) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }
      \vspace*{0.75em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
%        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(n,D'),\ipk_n,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        \textrm{Let \utrans be the transcript of $\langle \adv(\st),
          \Verify(\cdot,\cdot)\rangle$} \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
        \gets ExtractChain(\utrans) \\ 
        % D \cup \lbrace n+1 \rbrace)\rangle \\        
        \pcif \exists i \in [1,n]~\suchthat~
        \langle Show(\ipk_{i-1},\attrs(\cred_{i}),(i,D'),\cred_{i}), \\
        \hspace*{8em}Verify(\ipk_{i-1},(i,D')) \rangle
        = \langle \cdot,0\rangle \\%~\lor % \\
        % \pcind \attrs(\cred_i) \not\subseteq \attrs(\cred_{i-1}):
        \pcind \pcreturn 1 \\
%        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
%        \not\subseteq \ATTR[j])~\lor\\
%        \pcind level(\opk,n) = 0: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
    CU,HI,CI,Obtain,Issue,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
    \lbrace HU,CU,HI,CI,Obtain,Issue,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
    \gets \lbrace HU,CU,HI,CI,ObtIss,Issue,Show \rbrace$. $IssLor$ is equivalent
    to \OBTCHALb in \UAS, whereas $SigLor$ is equivalent to \CHALb. Also, \OWNR
    and \ATTR tables are essentially as in \secref{ssec:model-uas}. With $D =
    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
    which denotes the level of the credential used for authentication.}
  \label{fig:model-dac}  
\end{figure}

@@

\begin{enumerate}
\item The level $n$ of the credential they delegate.
\item Their public key \ipk.
\item An \UAS signature proving knowledge of a credential of level $n$, and over
  the attributes that this level-$n$ issuer is delegating.
\item The \ipk of the parent issuer.
\item Their $\fissue^{n,\dattrs}$ function.
\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
\end{enumerate}

We assume that, from an \ipk, it is possible to find the corresponding issuer
(e.g., using the previously mentioned public list). The mentioned
$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
Namely, the issuance function checks that the first requested attribute equals
$n+1$, and that all requested attributes are a subset of the attribute set
\dattrs being delegated by the level-$n$ issuer. In addition, signature
evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
must reveal the level of the credential used to produce the \UAS signature at
item 2, and reveal a set of attributes \dattrs that the level-$n$ issuer
delegates. Verifiers can then trivially check if the set of revealed attributes
are contained within the attributes delegatable by the parent issuer%
\footnote{Of course, additional checks may be added in both functions, this is
  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
that this structure creates.

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
    be replaced by any desired opening function.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
  include the attributes to delegate, and the credential level. It then
  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
  where $\ipk^{n-1}$ is the public key of the parent issuer,
  $\fissue^{n,\dattrs}$ is an issuance function as described in
  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
  delegate..
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
  credentials.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
  required by the issuer.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.] As in \CUASGen. Concretely, arbitrary
  \feval functions can be used -- not necessarily $\feval^{n,\dattrs}$.
\end{description}

>>>>

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key.
\end{description}

@@

\begin{theorem}[Anonymity of \CUASAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~ against anonymity of \CUASAC as defined in \cite{fhs19}, we build
  an adversary \advB against anonymity of \CUASGen as defined in
  \defref{def:sign-anonymity-uas}.

@@

\begin{theorem}[Unforgeability of \CUASAC]
  \label{thm:forge-cuasac}
  If the base \CUASGen construction has sign unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
\end{theorem}

@@

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from \CUASGen does not ensure privacy of the delegation
chain -- which could be achieved by making \feval output projective proofs like
in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
ensure that a (not top-level) issuer can only delegate attributes contained in a
credential it owns. Also, for simplicity, we restrict to the case of using one
credential per signature/interactive credential presentation, and assume that
all parties use the same opener and \finsp function.
%
The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
%
In the modelling for this setting, since there are multiple issuers, in addition
to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
issuers, and corrupt existing ones, respectively. The issuance and sign
anonymity properties are as before. For unforgeability, we still require
that no adversary can authenticate using a set of attributes that have not been
issued to a corrupt user. In addition, we require that for any possible
successful authentication protocol using a level-$n$ credential, we can extract
a chain of credentials of length $n$ such that each level-$i$ credential can
be used successfully to authenticate a level-$(i+1)$ credential up to the
level-$n$ credential, and that the attributes revealed in the level-$n$
authentication are contained in all the credentials up the chain.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }
      \vspace*{0.75em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(n,D'),\ipk_n,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        \textrm{Let \utrans be the transcript of $\langle \adv(\st),
          \Verify(\cdot,\cdot)\rangle$} \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
        \gets ExtractChain(\utrans) \\ 
        \pcif \exists i \in [1,n]~\suchthat~
        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
        \pcind D' \not\subseteq \ATTR[\iid]) \land
        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
    CU,HI,CI,Obtain,Issue,Obtiss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
    of the issuer with public key \ipk. With $D =
    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
    which denotes the level of the credential used for authentication.}
  \label{fig:model-dac}  
\end{figure}

@@

\begin{enumerate}
\item The level $n$ of the credential they delegate.
\item Their public key \ipk.
\item An \UAS signature proving knowledge of a credential of level $n$, and over
  the attributes that this level-$n$ issuer is delegating.
\item The \ipk of the parent issuer.
\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
\end{enumerate}

We assume that, from an \ipk, it is possible to find the corresponding issuer
(e.g., using the previously mentioned public list). The mentioned
$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
Namely, the issuance function checks that the first requested attribute equals
$n+1$, and that all requested attributes are a subset of the attribute set
\dattrs being delegated by the level-$n$ issuer. In addition, signature
evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
must reveal the level of the credential used to produce the \UAS signature at
item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
delegates. Verifiers can then trivially check if the set of revealed attributes
are contained within the attributes delegatable by the parent issuer%
\footnote{Additional checks may be added in both functions, but this is
  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
that this structure creates.

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
    be replaced by any desired opening function.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
  include the attributes to delegate, and the credential level. It then
  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
  where $\ipk^{n-1}$ is the public key of the parent issuer,
  $\fissue^{n,\dattrs}$ is an issuance function as described in
  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
  delegate..
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
  credentials.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
  required by the issuer.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
\end{description}

\paragraph{Security of \CUASDAC.} %
We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
anonymous issuance and signing, and has unforgeable issuance and signing.

\begin{theorem}[Issuance anonymity of \CUASDAC]
  If the base \CUASGen construction has issuance anonymity according to
  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
\end{theorem}

\begin{proof}
  Given \adv~ against issuance anonymity of \CUASDAC as defined in
  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
  ``translating'' the inputs from the former into inputs for the latter is
  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
  \advB with the  same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Signature anonymity of \CUASDAC]
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
\end{theorem}

\begin{proof}
  This is the same as in \thmref{thm:anon-cuasac}.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASAC]
  If the base \CUASGen construction has issuance and signature unforgeability
  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
  unforgeable AC scheme.
\end{theorem}

\begin{proof}
  First, we define the $ExtractChain(\utrans)$ function for our construction.
  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
    to transform non-interactive signature and verification in \UAS to interactive
    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
  fresh random number produced by the environment (acting as honest verifier),
  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
  credential and associated \ipk used to produce \Sig. Note that, for this
  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
  from \CUASGen, to get the credential one layer up in the chain.
  $ExtractChain$ repeats this step, until reaching the top level credential,
  issued by $\ipk_0$.

  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
  issuance and signing with their corresponding $\NIZKSetup$. Due to their
  zero-knowledge property, the resulting game is indistinguishable. Also, note
  that $ExtractChain$ succeeds to extract the corresponding credential chain,
  due to simulation extractability of the NIZKs.

  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
  delegation chain that makes \adv~win at line 10. This means that an
  uncorrupted issuer at position $i-1$ of the chain did not own a credential
  containing $D'$, but the issuer at position $i$ does. Then, either of the
  following must happen:

  \begin{itemize}
  \item The credential of the issuer at position $i$ is a forgery, meaning that
    it is a valid signature by the issuer at position $i-1$, who did not produce
    it. This can be used to break signature non-frameability of \CUASGen.
  \item The credential of the issuer at position $i$ is not a forgery, meaning
    that it is a valid signature by the issuer at position $i-1$, who produced
    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
    and therefore breaks issuance unforgeability of \CUASGen.
  \end{itemize}
  %
  \qed
\end{proof}
